---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

Setting global options for chunks and knitr

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval = FALSE)
```

Load packages needed

```{r}

library(devtools)
library(sinew)

```
 
Initialize a new package 
 
```{r}

devtools::create('test')
knitr::opts_knit$set(root.dir = 'test')
```
 
Add some basics: Package License and `data_raw` subdirectory 
 
```{r}

devtools::use_mit_license('test')
devtools::use_data_raw('test')

```

Write the toy functions to `data_raw/test.R`

```{r}
 
cat('xx <- function(data){
    mutate(data,mpg2 = mpg^2)
}

#some comment
yy <- function(a=4){
  head(runif(10),a)
  # a comment
}

zz <- function(v=10,a=8){
  head(runif(v),a)
}

yy(6)

zz(30,3)

xx()
',sep='\n',file='test/data-raw/test.R') 

```

What does the RStudio skeleton look like? 

`Shift+Alt+Cmd+R` (macOS)

```{r RStudio skeleton, eval=FALSE}

#' Title
#'
#' @param a 
#'
#' @return
#' @export
#'
#' @examples
yy <- function(a=4){
  head(runif(10),a)
  # a comment
}

```

Split the `tests/data-raw/test.R` into single R files in the `test/R` subdirectory

```{r}
sinew::untangle(file = 'test/data-raw/test.R',dir.out = 'test/R',keep.body = FALSE)
```
 
Append the appropriate namespaces to the functions 
 
```{r}

sinew::pretty_namespace(con = 'test/R/xx.R')

sinew::pretty_namespace(con = 'test/R',overwrite = TRUE)

```

Create sinew roxygen2 skeletons populated with information from within the functions. 

And replace the placeholders with information.

```{r}

sinew::makeOxyFile(input = 'test/R/yy.R',overwrite = FALSE)

file.remove('test/R/oxy-yy.R')

sinew::makeOxyFile(input = 'test/R',overwrite = TRUE)

```

Append to the `DESCRIPTION` file the the `imports` field

```{r DESCRIPTION}

sinew::makeImport('test/R',format = 'description',desc_loc = 'test')

rstudioapi::navigateToFile('test/DESCRIPTION')

```

Looking back `yy` should have a summary function

```{r, eval=FALSE}

yy <- function(a=4,b=2){
  
  x <- utils::head(stats::runif(10*b),a)
  
  stats::quantile(x,probs=.95)
  
  # a comment
}

```

Now the roxygen2 header is not in synch with the function. Use `sinew::moga` to update the roxygen2 header with new formals and import fields. Make Oxygen Great Again (moga)

```{r MOGA}

sinew::moga(path = 'test/R/yy.r',overwrite = FALSE)

sinew::moga(path = 'test/R/yy.r',overwrite = FALSE,force.fields = 'seealso')

sinew::moga(path = 'test/R/yy.r',overwrite = TRUE,force.fields = 'seealso')

```

Compile the roxygen2 headers into Rd files in `man` and update the `NAMESPACE` file

```{r OXYGENIZE}

devtools::document(pkg = 'test')

```

Run `R CMD check --as-cran`

```{r CHECK}

devtools::check(pkg = 'test',cran = TRUE)

```

A problem that ussually arises when checking pacakges that use tidyverse is 'undefined global functions'. To resolve this issue you need to use {rlang} functions. 

To make this an easy process we use {tidycheckUsage} which creates a tidy output of the portion of the R CMD check output that checks for the global variables, and lets you append the correct rlang functions to solve this issue. 

```{r}
library(tidycheckUsage)
tidycheckUsagePackage('test')

append_rlang_package('test')

rstudioapi::navigateToFile('test/R/xx.R')

# refresh the documentation
sinew::moga('test/R/xx.R',overwrite = TRUE)
sinew::makeImport(script = 'test/R',format = 'description',desc_loc = 'test')

devtools::document('test')

# recheck the package
devtools::check('test')

```

Install the package, look at the documentation and run the functions.

```{r test functions}

devtools::install('test')

library(test)

?test::xx

?test::yy

?test::zz

test::xx(mtcars)

test::yy()

test::zz()

```

Interactive sinew

```{r interactive}

rstudioapi::navigateToFile('test/R/yy.R')

```
